Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-09 paper/paper.tex
Include plots in report
Include table with positional error statistics
Remove test image from report
Add building match example images

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{test_image}
\caption{En typisk rymdhiss enligt Wikipedia. Bildkälla (\cite{sampleitem1}).}
\label{fig:space}
\end{figure}

@@

% TODO: Figure: Overlapping buildings, OSM-SLU, 1:1
% TODO: Figure: Overlapping buildings, OSM-SLU, 1:n

@@

\subsection{Positional offset statistics}

@@

% TODO: Bar plot positional accuracy
% TODO: Bar plot turning functions

>>>>

@@

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_match_1_1}
\caption{An example of a 1:1 building match, where the sought-after building was found both in the OSM (red) and SLU (blue) datasets.}
\label{fig:space}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_match_1_n}
\caption{An example of a 1:n building match, where the sought-after building was represented as one polygon in the OSM (red) dataset, but divided into many smaller lots in the SLU (multicolored) dataset.}
\label{fig:space}
\end{figure}

@@

\subsection{Positional accuracy statistics}

\begin{table}[H]
\begin{tabular}{lllll}
    $e_{average}$ & $e_{max}$ & $e_{min}$ & $e_{standard deviation}$ \\
    2.0579... & 9.9878... & 0.0 & 1.2464...
\end{tabular}
\end{table}

@@

% Bar plot positional accuracy

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_pos_error_plot}
\caption{The average positional accuracies per building as a frequency diagram.}
\label{fig:space}
\end{figure}

\subsection{Shape accuracy statistics}

% Bar plot turning functions

\begin{figure}[H]
\centering
\includegraphics[height=0.5\textheight]{img_turning_function_plot}
\caption{The turning function distances between 1:1 building pairs as a frequency diagram.}
\label{fig:space}
\end{figure}
